\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=2cm, bottom=4.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{derivative}
\usepackage[thinc]{esdiff}
\usepackage{amsmath}
\usepackage{tcolorbox}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{accents}
\usepackage{float}
\usepackage[utf8]{inputenc}

% Default fixed font does not support bold face
\DeclareFixedFont{\ttb}{T1}{txtt}{bx}{n}{12} % for bold
\DeclareFixedFont{\ttm}{T1}{txtt}{m}{n}{12}  % for normal

% Custom colors
\usepackage{color}
\definecolor{deepblue}{rgb}{0,0,0.5}
\definecolor{deepred}{rgb}{0.6,0,0}
\definecolor{deepgreen}{rgb}{0,0.5,0}

\usepackage{listings}

% Python style for highlighting
\newcommand\pythonstyle{\lstset{
language=Python,
basicstyle=\ttm,
morekeywords={self},              % Add keywords here
keywordstyle=\ttb\color{deepblue},
emph={MyClass,__init__},          % Custom highlighting
emphstyle=\ttb\color{deepred},    % Custom highlighting style
stringstyle=\color{deepgreen},
frame=tb,                         % Any extra options here
showstringspaces=false
}}


% Python environment
\lstnewenvironment{python}[1][]
{
\pythonstyle
\lstset{#1}
}
{}

\hypersetup{%
  colorlinks=true,
  linkcolor=blue,
  linkbordercolor={0 0 1}
}
 
\renewcommand\lstlistingname{Algorithm}
\renewcommand\lstlistlistingname{Algorithms}
\def\lstlistingautorefname{Alg.}

\lstdefinestyle{Python}{
    language        = Python,
    frame           = lines, 
    basicstyle      = \footnotesize,
    keywordstyle    = \color{blue},
    stringstyle     = \color{green},
    commentstyle    = \color{red}\ttfamily
}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

% Edit these as appropriate
\newcommand\course{ECE460J}
\newcommand\hwnumber{2}                  % <-- homework number
\newcommand\NetIDa{\small Sidharth Babu, Laith Altarabishi}           % <-- NetID of person #1
\newcommand\NetIDb{\small Afnan Mir, Jonathan Vasilyev}
\newenvironment{solution}
  {\renewcommand\qedsymbol{$\blacksquare$}
  \begin{proof}[Solution]}
  {\end{proof}}
\renewcommand\qedsymbol{$\blacksquare$}
\newcommand{\ubar}[1]{\underaccent{\bar}{#1}}

\pagestyle{fancyplain}
\headheight 35pt
% \lhead{\NetIDa}
\lhead{\NetIDb \\\NetIDa} % <-- Comment this line out for problem sets (make sure you are person #1)
\chead{\textbf{\Large Project Proposal}}
\rhead{\small \course \\ \today}
\lfoot{}
\cfoot{}
\rfoot{\small\thepage}
\headsep 1.5em
\begin{document}
\section*{Objective}
LoFi music is an important part of almost every college students study routine, especially in our major. For our project, we would like to
build and train a deep learning model that will be able to generate new LoFi music after listening to a dataset of already created LoFi music. We are 
planning on building this model from the ground up, meaning no pretrained model will be used. We plan on building a model that will be able to take in and
output sequential data, whether that be an RNN-LSTM model or a transformer model. 

\section*{Dataset}
We have found \href{https://github.com/nmtremblay/lofi-samples}{this} dataset on github that contains over one hundred .midi files for LoFi music. We plan on using the sequences of notes and chords in these .midi files to predict
the next note in the sequence. With this, we can get a new sequence of notes and chords that will represent a new LoFi song.
\end{document}